Interval Probability for Fuzzy Quantum Theories

### 2016-08-06 prob.tex
prob.tex Modifying sentences...

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure~\cite{Nikodym1930,Folland2013}, or just
called the Radon-Nikodym derivative of $\pmeas$ because we are always
with respect to the counting measure. The Radon-Nikodym theorem states
that the converse is also true.

@@

In a strict computational or experimental setting, one may question
the reliance of the definition of probability space on the uncountable
and uncomputable real interval $[0,1]$. This interval includes numbers
like $0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending
on whether Turing machine $M_{i}$ halts or not. Such numbers cannot
be computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. % \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
% Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
% using base 16 directly.}
Therefore, in a resource-aware computational or experimental setting,
it is more appropriate to consider probability measures that map events
to a set of elements computable with a fixed set of resources. We
expand on this observation and then consider %% two approaches from the literature: set-valued probability
%% measures~\cite{Artstein1972,PuriRalescu1983} and 
interval-valued probability measures~\cite{Weichselberger2000,JamisonLodwick2004}
in detail.\footnote{There is another possible approach that can be used to split the real
interval $[0,1]$ into a collection of subsets~\cite{PuriRalescu1983}
\amr{need to explain the connection and why we are not using it.}}

@@

In previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, although the exact value of $\pmeas(E)$
may not be known, we could still assume each event has a probability.
If we want to know its value, we can run $N$ independent trials.
Let $x_{i}$ denote whether the event~$E$ occurs in the $i$-th
trial or not, then $\pmeas(E)$ could be approximated to given accuracy
by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability
converging to one as $N$ goes to infinity. This fact is called the
law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

>>>>

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum\rho(\omega)=1$,
and $\rho$ is called the Radon-Nikodym derivative of $\pmeas$ (with
respect to the counting measure)~\cite{Nikodym1930,Folland2013}.
The converse is also valid and called the Radon-Nikodym theorem.

@@

In a strict computational or experimental setting, one may question
the reliance of the definition of probability space on the uncountable
and uncomputable real interval $[0,1]$. This interval includes numbers
like $0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending
on whether Turing machine $M_{i}$ halts or not. Such numbers cannot
be computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. % \yutsung{Check the meaning of the ``computing $\frac{\pi}{4}$'', because
% Bailey Borwein Plouffe formula can computing the $n$th binary digit of $\pi$ 
% using base 16 directly.}
Therefore, in a resource-aware computational or experimental setting,
it is more appropriate to consider probability measures that map events
to a set of elements computable with a fixed set of resources. We
expand on this observation and then consider %% two approaches from the literature: set-valued probability
%% measures~\cite{Artstein1972,PuriRalescu1983} and 
interval-valued probability measures~\cite{Weichselberger2000,JamisonLodwick2004}
in detail.

@@

In the previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, the probability of each event is assumed
to exist although the exact value of $\pmeas(E)$ may not be known.
If we want to know its value, we can run $N$ independent trials.
Let $x_{i}$ denote whether the event~$E$ occurs in the $i$-th
trial or not, then $\pmeas(E)$ could be approximated to given accuracy
by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability
converging to one as $N$ goes to infinity. This fact is called the
law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
